---
title: "Exercises 1 Vectors"
output:
  pdf_document: default
  html_notebook: default
---
#### MA615 Nanfang_Hong (U92430309)

##### 1. Create the vectors:
  
  (a)
```{r}
1:20
```
  
  (b)
```{r}
20:1
```
  
  (c)
```{r}
c(1:19, 20, 19:1)
```
  
  (d)
```{r}
tmp <- c(4, 6, 3)
tmp
```
  
  (e)
```{r}
rep(tmp, times = 10)
```
  
  (f)
```{r}
rep(tmp, length = 31)
```
  
  (g)
```{r}
c(rep(4, 10), rep(6, 20), rep(3, 30))
```
  

##### 2. Create a vector of the values of e^x^cos(x) at x = 3,3.1,3.2,...,6.
```{r}
x = seq(3, 6, 0.1)
c(exp(x) * cos(x))
```

##### 3. Create the following vectors:
  (a)
```{r}
i <- 1:34
c(0.1 ^ (i + 2) * 0.2 ^ i)
```
  (b)
```{r}
i <- 1:25
c(2 ^ i / i)
```
  
##### 4. Calculate the following:
  (a)
```{r}
i <- (10:100)
sum(i^3 + 4*i^2)
```
  (b)
```{r}
i <- 1:25
sum((2 ^ i) / i + (3 ^ i) / (i ^ 2))
```

##### 5. Use the function paste to create the following character vectors of length 30:
  (a)
```{r}
paste(c("label"), 1:30)
```
  (b)
```{r}
paste(c("fn"), 1:30, sep = "")
```
  
##### 6. Execute the following lines which create two vectors of random integers which are chosen with replacement from the integers 0, 1, . . . , 999. Both vectors have length 250.

```{r}
set.seed(50)
xVec <- sample(0:999, 250, replace=T)
yVec <- sample(0:999, 250, replace=T)
xVec
yVec
```
  
  (a)
```{r}
i <- 2:250
c(yVec[i]-xVec[i - 1])
```
  (b)
```{r}
c(sin(yVec[i - 1]) / cos(xVec[i]))
```
  (c)
```{r}
i <- 3:250
c(xVec[i - 2] + 2 * xVec[i - 1] - xVec[i])
```
  (d)
```{r}
i <- 1:249
sum(exp(-xVec[i + 1]) / (xVec[i] + 10))
```
  
##### 7. This question uses the vectors xVec and yVec created in the previous question and the functions sort, order, mean, sqrt, sum and abs.

  (a)
```{r}
yVec[yVec > 600]
```
  (b)
```{r}
yVec_600 <- yVec # Duplicate yVec to yVec_600. 
yVec_600[yVec_600 <= 600] <- NA # Replace 600 or less with NA
order(yVec_600, na.last = NA) # Positions in yVec with values >600 (in acsending sequence)
```
  (c)
```{r}
xVec[order(yVec_600, na.last = NA)]
```
  (d)
```{r}
xVec_mean = mean(xVec)
c(sqrt(abs(xVec - xVec_mean)))
```
  (e)
```{r}
sum(yVec >= (max(yVec) - 200))
```
  (f)
```{r}
sum(xVec %% 2 == 0) # Integer division by 2. divisible -> 0, non-divisible -> 1. 
```
  (g)
```{r}
xVec[order(yVec)]
```
  (h)
```{r}
i <- seq(1, 3 * ceiling(length(xVec)/3) -2, 3) # 1, 4, 7, ...
yVec[i]
```
##### 8. By using the function cumprod or otherwise, calculate

```{r}
i <- 1:19
1 + sum(cumprod(2 * i) / cumprod(2 * i + 1)) 
```

  